---
title: "Cable Theft Insight"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    orientation: rows
    logo: logo.png
    #social: [ "twitter", "facebook"]
    #navbar:
    #  - { title: "About", href: "http://data-laborer.eu", align: right }
    #source_code: "https://github.com/YvesCR/flexocpu"
---

<script src="inst/www/jquery-1.10.2.min.js"> </script>
<script src="inst/www/opencpu-0.4.js"> </script>

<script> 

$(function(){
    
  var paramid = 1;

  $('#myBtn').click( function () {
    
    $('#myBtn').hide();
    $('iframe').css({'display': 'inline'}); 
    
    var req2 = ocpu.call("make_map", {
        title : 'Chez Mamie:\n Best canteen of London'
      }, function(session){
        $('iframe').attr('src', session.getFileURL('mymap.html'));
      });
  });

  var jsonReqtime = ocpu.call("gethowel",{
      		id : Number(paramid)
      	}, function(session){
      	
      	session.getObject(function(outtxt){
      		$("#json_output").text(outtxt);
      		
      		var age_json = outtxt[0]["age"];
      		$('#age .value').text(age_json);
      		 if (age_json <= 21) {var color_age = '#01bb69';
      		  } else if (age_json <= 60) {var color_age = '#ff8039';
      	      } else {var color_age = '#fb305a';}
      		$('#age').css("background-color", color_age);
      		
      		var height_json = outtxt[0]["height"];
      		$('#height .value').text(height_json);
      		 if (height_json <= 140) {var color_income = '#ff8039';
      		  } else if (height_json >= 160) {var color_income = '#fb305a';
      	      } else {var color_income = '#01bb69';}
      		$('#height').css("background-color", color_income);
      		
      		var weight_json = outtxt[0]["weight"];
      		$('#weight .value').text(weight_json);
      		 if (weight_json <= 20) {var color_asset = '#ff8039';
      		  } else if (weight_json <= 40) {var color_asset = '#fb305a';
      	      } else {var color_asset = '#01bb69';}
      		$('#weight').css("background-color", color_asset);
      		
      		$('#id .value').text(outtxt[0]["id"]);
      		
      		var male_json = outtxt[0]["male"];
      		$('#sex .value').text(male_json);
      			 if (male_json === 0) {var color_male = '#ae6df8';
      		  } else {var color_male = '#02a8ee';}
      		$('#sex').css("background-color", color_male);
      		
      	});
  });
  
  var req = $("#plotdiv").rplot("plotind", {id : Number(paramid)});

});

$(function(){
  $("#idsubmit").click(function(e){
  
  var paramid = $("#myid").val();
  
  var jsonReqtime = ocpu.call("gethowel",{
    		id : Number(paramid)
    	}, function(session){
    	
    	session.getObject(function(outtxt){
    		$("#json_output").text(outtxt);
    		
      		var age_json = outtxt[0]["age"];
      		$('#age .value').text(age_json);
      		 if (age_json <= 21) {var color_age = '#01bb69';
      		  } else if (age_json <= 60) {var color_age = '#ff8039';
      	      } else {var color_age = '#fb305a';}
      		$('#age').css("background-color", color_age);
      		
      		var height_json = outtxt[0]["height"];
      		$('#height .value').text(height_json);
      		 if (height_json <= 140) {var color_income = '#ff8039';
      		  } else if (height_json >= 160) {var color_income = '#fb305a';
      	      } else {var color_income = '#01bb69';}
      		$('#height').css("background-color", color_income);
      		
      		var weight_json = outtxt[0]["weight"];
      		$('#weight .value').text(weight_json);
      		 if (weight_json <= 20) {var color_asset = '#ff8039';
      		  } else if (weight_json <= 40) {var color_asset = '#fb305a';
      	      } else {var color_asset = '#01bb69';}
      		$('#weight').css("background-color", color_asset);
      		
      		$('#id .value').text(outtxt[0]["id"]);
      		
      		var male_json = outtxt[0]["male"];
      		$('#sex .value').text(male_json);
      			 if (male_json === 0) {var color_male = '#ae6df8';
      		  } else {var color_male = '#02a8ee';}
      		$('#sex').css("background-color", color_male);
      		    		
    	});
    });
    
    var req = $("#plotdiv").rplot("plotind", {id : Number(paramid)});

  });

});
  
</script>

```{r setup, include=FALSE}
# devtools::install_github("Rstudio/flexdashboard")
library(flexdashboard)
```



Data Exploration
===================================== 

Row {data-height=300}
-----------------------------------------------------------------------

### Age Height by Sex

```{r, fig.width=15}
data("howell")

ggplot2::ggplot(data = howell, ggplot2::aes(x = age, y = height, color = as.factor(male))) +
  ggplot2::geom_point()
```

### Age Weight by Sexx

```{r, fig.width=15}
data("howell")

ggplot2::ggplot(data = howell, ggplot2::aes(x = age, y = weight, color = as.factor(male))) +
  ggplot2::geom_point()
```







Predictive Model
===================================== 

Row {data-height=200}
-------------------------------------

### Predictions {data-width=200}

<input type="integer" class="form-control" id="myid" value="1" style = "width: 90%;">

<button type="submit" id="idsubmit" class="btn btn-default">Update dashboard!</button>


### Definition {data-width=800}

Click the update button for the latest predictions of cable theft incidents, knowing various factors such as weather, protective service patrolling numbers as well as protest action counts. Below is an Arima model output that accounts for various regressors mentioned here.   


 
Row {data-height=200}
-----------------------------------------------------------------------

### Municipal Protests

```{r valuebox1}
valueBox(3, icon = "fa-pencil", color = '#01bb69')
```

### Protective Service Patrols

```{r valuebox2}
valueBox(4, icon = "fa-envelope-o", color = '#ff8039')
```


Row {data-height=200}
-----------------------------------------------------------------------

### Month 1 Prediction

```{r}
gauge(105, min = 0, max = 100, gaugeSectors(
  success = c(80, 200), warning = c(40, 79), danger = c(0, 39)
))
```

### Month 2 Prediction

```{r}
gauge(110, min = 0, max = 100, gaugeSectors(
  success = c(80, 200), warning = c(21, 40), danger = c(0, 20)
))
```

### Month 3 Prediction

```{r}
gauge(125, min = 0, max = 100, gaugeSectors(
  success = c(80, 200), warning = c(3, 6), danger = c(7, 10)
))
```

Row {data-height=400}
-----------------------------------------------------------------------

### Age Height by Sex

```{r, fig.width=15}
data <- "Date Incidents NumberProtests NumberPatrols
11/30/2014   132   3   2
  12/31/2014   152  1  3
  1/31/2015   156  2  4
  2/28/2015   145  4  2
  3/31/2015   136  3  2
  4/30/2015   126  2  4
  5/31/2015   125  3  6
  6/30/2015   143  1  7
  7/31/2015   115  2  6
  8/31/2015   121  2  3
  9/30/2015   127  1  6
  10/31/2015   121  3  5
  11/30/2015   118  1  8
  12/31/2015   109  1  9"
  library(xts)
  # use fill=TRUE because you only provided data for 4 composites
  allcomp <- read.table(text=data, header=TRUE, fill=TRUE)
  # create an xts object from the remaining data
  allcomp$Date <- as.Date(allcomp[,1], "%m/%d/%Y")
  allcomp_xts <- xts(allcomp[,-1], as.Date(allcomp[,1], "%m/%d/%Y"))

  fit <- arima(allcomp_xts$Incidents, order=c(1,0,0), list(order=c(2,1,0)))
  fore <- predict(fit, n.ahead=2)
  # error bounds at 95% confidence level
  U <- fore$pred + 2*fore$se
  L <- fore$pred - 2*fore$se
  ts.plot(ts(allcomp_xts$Incidents), fore$pred, U, L, col=c(1,2,4,4), lty = c(1,1,2,2))
  legend("topleft", c("Actual", "Forecast", "Error Bounds (95% Confidence)"), col=c(1,2,4), lty=c(1,1,2))
  
```





Prescribed Actions
===================================== 

Row {data-height=300}
-----------------------------------------------------------------------

### Age Height by Sex

Row {data-height=700}
-----------------------------------------------------------------------

### Mapping

<button type="button" id="myBtn" >Map</button>

<iframe src="about:blank" style='height: 620px;width: 1300px;display: none;'></iframe>


